Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-23 paper/ijcai/paper.tex
initial pass on RQ3

\begin{table*}[h]
	\small
	% \setlength{\tabcolsep}{3pt}
	\centering
	  \begin{tabular}{l|cccc|cccc|c}
		\toprule
		\multirow{2}{*}{Project}            & \multicolumn{4}{c|}{\sfl{}$^{k}$}  & \multicolumn{4}{c|}{\combpar{k}} & \multirow{2}{*}{\# Faults} \\

@@

@@

\Mar{metric only used here...revise}
\Fix{
We compared \combpar{5} and \combpar{10} against
\sfl{}$^{5}$ and \sfl{}$^{10}$ using the commonly used metric $\Delta{}C =
C(\textrm{SFL$^{k}$}) - C(\textrm{\combpar{k}})$, where $C$ is the cost of
diagnosis. $C$ is the mean ranking of all buggy statements. $\Delta C >0$ means
that the position of the faulty statement has decreased in the ranking after
applying the \combpar{k} approach. Hence, reducing the cost of locating the bug.
$\Delta C <0$ means that the faulty statement may be removed by \combpar{k}.
$\Delta C=0$ means that the faulty statement remained in the same position.  We
also assume a perfect bug understanding, i.e., if the developer sees the bug in
the ranking, he can say it is the faulty one.
}

In \textbf{RQ3}, we intend to evaluate the impact of combining \ds{} with \sfl{}
to improve fault localization. For each fault, we calculated the cost of diagnosis
$\Delta{}C$ between \sfl{}$^{k}$ and \combpar{k} for both variants $k = 5$ and $k=10$.

>>>>

\begin{table*}[t!]
	\small
	% \setlength{\tabcolsep}{3pt}
	\centering
	  \begin{tabular}{l|cccc|cccc|c}
		\toprule
		\multirow{2}{*}{Project}            & \multicolumn{4}{c|}{\sfl{}$^{k}$}  & \multicolumn{4}{c|}{\combpar{k}} & \multirow{2}{*}{\# Faults} \\

@@

In \textbf{RQ3}, we evaluate the effective impact of combining \ds{}
with \sfl{} to improve fault localization.

The first experiment we ran to assess impact consisted of measuring
the \emph{difference of diagnosis cost}. This metric has been
previously used in other studies~\Fix{cite cite}. More specifically,
we computed $\Delta{}C = C(\textrm{SFL$^{k}$}) -
C(\textrm{\combpar{k}})$, where $C$ denotes the diagnosis cost and is
obtained by computing the mean position in the ranking of all buggy
statements. $\Delta C >0$ means that the position of the faulty
statement has decreased with \combpar{k}, \ie{}, the combination had a
positive impact. $\Delta C <0$ means that \combpar{k} performs worse
compared to its baseline. That could happen if dynamic slicing misses
the faulty statement---the statements not included in the slice will
have their suspiciousness scores reduced and ranks potentially
reduced. $\Delta C=0$ means that the faulty statement remained in the
same position.  It is worth noting that we assume a perfect bug
understanding, i.e., if the developer sees the bug in the ranking, he
is able to precisely determine if it is the faulty one.

\Mar{I see there are different results/metrics/tables. We need to
  organize this better, with sub-questions or stating different
  other experiments to answer the main question.}

@@
